Relocating a Cluster of Earthquakes Using a Single Seismic Station

### 2013-08-03 paper2/paper2.tex
last lot of changes as requested by the BSSA editorial team upon acceptance

\vspace{2em}
\begin{centering}
\section*{Abstract}
\end{centering}
Coda-waves arise from scattering to form the later arriving
components of a seismogram. Coda-wave interferometry is an emerging
tool for constraining earthquake source properties from the
intereference pattern of coda-waves between nearby events. A new
earthquake location algorithm is derived which relies on coda-wave
based probabilistic estimates of earthquake separation. The
algorithm can be used with cod-waves alone or in tandem with arrival-time 
data. Synthetic examples in 2D and 3D and real earthquakes on
the Calaveras Fault, California are used to demonstrate the
potential of coda-waves for locating poorly recorded earthquakes. It
is demonstrated that coda-wave interferometry: (a) outperforms
traditional earthquake location techniques when the number of
stations is small; (b) is self-consistent across a broad range of
station situations; and (c) can be used with a single station to
locate earthquakes.

@@

Coda-wave interferometry offers a new technique for understanding
earthquakes in intraplate areas with sparse networks and poor
azimuthal coverage. In particular, the ability to combine coda-wave
constraints with arrival-times makes it possible to link well
constrained events from a temporary deployment with those recorded
outside the deployment period. All that is required to achieve this
is at least one network station which has recorded sufficient events
from both periods. CWI facilitates the location of poorly recorded
events to an accuracy approaching those recorded during the
temporary deployment and therefore opens new avenues for imaging
intraplate fault structures and improving our understanding of
intraplate seismicity and earthquake hazard. Importantly, this analysis 
can be conducted for any historical aftershock sequence or earthquake swarm
recorded by a temporay deployment, Our technique is, in that sense, related
to the retorspective sesimological observation technique of 
\citet{dr_Curtis12a_EPSL} that utilizes interferometry to obtain seismic signals
on newly installed sensors regardless of whether the event occurs before, 
during or after the physical installation of the sensor.

@@

%%=======================================================================================
% Table 2

\begin{table}
\caption[Conditions for identifying unsuitable waveforms when
applying CWI] {Conditions used to identify unsuitable waveforms
before applying CWI \citep[Originally published as Table
5][]{dr_Robinson11a}} \label{tab:-conditions4unsuitablewaveform}
\begin{tabular}{|l|p{0.7\textwidth}|}
\hline
 & \textbf{condition} \\
\hline
1 & waveform is clearly corrupted \\
2 & waveform indicates recording of more then one event \\
3 & signal to noise ratio is obviously low \\
4 & there is insufficient coda recorded after the \\
 & first arrivals \\
5 & there is insufficient recording before the arrivals \\
 &  (needed for accurate noise energy estimate) \\
\hline
\end{tabular}
\end{table}

>>>>

\vspace{2em}
\begin{centering}
\section*{Abstract}
\end{centering}
Coda-waves arise from scattering to form the later arriving
components of a seismogram. Coda-wave interferometry is an emerging
tool for constraining earthquake source properties from the
intereference pattern of coda-waves between nearby events. A new
earthquake location algorithm is derived which relies on coda-wave
based probabilistic estimates of earthquake separation. The
algorithm can be used with cod-waves alone or in tandem with arrival-time 
data. Synthetic examples (2D and 3D) and real earthquakes on
the Calaveras Fault, California are used to demonstrate the
potential of coda-waves for locating poorly recorded earthquakes. It
is demonstrated that coda-wave interferometry: (a) outperforms
traditional earthquake location techniques when the number of
stations is small; (b) is self-consistent across a broad range of
station situations; and (c) can be used with a single station to
locate earthquakes.

@@

Coda-wave interferometry offers a new technique for understanding
earthquakes in intraplate areas with sparse networks and poor
azimuthal coverage. In particular, the ability to combine coda-wave
constraints with arrival-times makes it possible to link well
constrained events from a temporary deployment with those recorded
outside the deployment period. All that is required to achieve this
is at least one network station which has recorded sufficient events
from both periods. CWI facilitates the location of poorly recorded
events to an accuracy approaching those recorded during the
temporary deployment and therefore opens new avenues for imaging
intraplate fault structures and improving our understanding of
intraplate seismicity and earthquake hazard. Importantly, this analysis 
can be conducted for any historical aftershock sequence or earthquake swarm
recorded by a temporay deployment. Our technique is, in that sense, related
to the retrospective seismological observation technique of 
\citet{dr_Curtis12a_EPSL} that utilizes interferometry to obtain seismic signals
on newly installed sensors regardless of whether the event occurs before, 
during or after the physical installation of the sensor.

@@

%%=======================================================================================
% Table 2
\clearpage
\begin{table}[h]
\caption[Conditions for identifying unsuitable waveforms when
applying CWI] {Conditions used to identify unsuitable waveforms
before applying CWI$^*$} \label{tab:-conditions4unsuitablewaveform}
\begin{tabular}{|l|p{0.7\textwidth}|}
\hline
 & \textbf{condition} \\
\hline
1 & waveform is clearly corrupted \\
2 & waveform indicates recording of more then one event \\
3 & signal to noise ratio is obviously low \\
4 & there is insufficient coda recorded after the \\
 & first arrivals \\
5 & there is insufficient recording before the arrivals \\
 &  (needed for accurate noise energy estimate) \\
\hline
\end{tabular}
\end{table}
$^*$ Originally published as Table
5 in \citet{dr_Robinson11a}
